Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-02-24 article/figures.Rmd
+ fixes to supp material and figures

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap='The relationship between surrogates and genetic variation secured in prioritizations. Panel (a) shows the relationship between environmental surrogates and adaptive genetic variation. Panel (b) shows that for geographic surrogates and neutral genetic variation. Transparent gray lines denote trends for each species, and black lines show general trends across all species.'}
### prepare data frames for plotting
#env.correlation.PDF <- filter(correlation.DF, Type='Environmental')
#
#%>% left_join(
#		data.frame(
#			letter=unname(toupper(cld(full.model.GLHT)$mcletters$Letters)),
#			Combination=as.character(names(toupper(cld(full.model.GLHT)$mcletters$Letters)))
#		) %>% mutate(Combination=as.character(Combination)),
#		by='Combination'
#	) %>% data.frame()

#geo.correlation.PDF <- filter(correlation.DF, Type='Geographic')
### make plots
#suppressWarnings({
#	p1 <- ggplot() +
#		geom_boxplot(aes(x=Surrogate.target, y=genetic.held, color=Method, group=Method), data=env.correlation.DF) +
#		geom_text(aes(x=Surrogate.target, y=letter.height, label=letter),
#			data=results.PDF, position=position_dodge(0.9)) +
#		geom_text(aes(x=0.6, y=1.03, label='(a)')) +
#		xlab('Environmental variation secured (%)') +
#		ylab('Adaptive genetic\nvariation secured (%)') +
#		theme_classic()
#	p2 <- ggplot() +
#		geom_boxplot(aes(x=Surrogate.target, y=neutral.held, color=Method), data=geo.correlation.DF) +
#		geom_text(aes(x=Surrogate.target, y=letter.height, label=letter),
#			data=results.PDF, position=position_dodge(0.9)) +
#		geom_text(aes(x=0.6, y=1.03, label='(b)')) +
#		xlab('Geographic variation secured (%)') +
#		ylab('Neutral genetic\nvariation secured (%)') +
#		theme_classic()
#	grid.arrange(p1, p2, nrow=1)
# })

plot(1)

>>>>

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap='The relationship between surrogates and genetic variation secured in prioritizations. Panel (a) shows the relationship between environmental surrogates and adaptive genetic variation. Panel (b) shows that for geographic surrogates and neutral genetic variation. Box-plots show variation in the proportion of genetic variation secured using different surrogate-based targets. Lines show the general trends.'}
# make figure
p1 <- ggplot(mapping=aes(x=factor(Surrogate.target),y=genetic.held, color=Method)) +
	geom_boxplot(data=env.correlation.DF) +
	xlab('Environmental surrogate target (%)') + 
	ylab('Adaptive genetic variation secured (%)') +
	geom_text(aes(x=0.05, y=0.9, label='(a)')) +
	geom_line(data=data.frame(summarize(group_by(env.correlation.DF, Surrogate.target, Method), genetic.held=mean(genetic.held)))) +
	scale_color_manual(name='Prioritization', values=c('Optimal'='black', 'Random'='grey50'))

p2 <- ggplot2(mapping=aes(x=factor(Surrogate.target),y=genetic.held, color=Method)) +
	geom_boxplot(data=geo.correlation.DF) +
	xlab('Geographic surrogate target (%)') + 
	ylab('Neutral genetic variation secured (%)') +
	geom_text(aes(x=0.05, y=0.9, label='(b)')) +
	geom_line(data=data.frame(summarize(group_by(geo.correlation.DF, Surrogate.target, Method), genetic.held=mean(genetic.held)))) +
	theme_classic() +
	scale_color_manual(name='Prioritization', values=c('Optimal'='black', 'Random'='grey50'))

# render figure
grid.arrange(p1,p2,nrow=1)

### 2016-02-24 article/supporting_information.Rmd
+ fixes to supp material and figures

```{r, echo=FALSE, fig.width=9.5, fig.height=10, out.width='7.5in', out.height='8.5in', fig.cap='Species distributions. Squares represent planning units. For a given species, planning units that were found to be inhabited are denoted with bright blue.'}
## plot map of species distributions
# fortify data
spp.grid.FPLY <- ldply(unique(spp.samples.DF$species), function(x) {
		z <- grid.FPLY[,c('long', 'lat', 'group', x),drop=FALSE]
		names(z)[4] <- 'presence'
		z$species <- gsub('\\_', ' ', x)
		return(z)
	}
)
# plot species data
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spp.grid.FPLY, aes(x=long, y=lat, 
		group=group, fill=presence), alpha=0.8, color='grey10') +
	theme_classic() +
	guides(fill=guide_legend(title='Presence')) +
	theme(
		line = element_blank(), rect = element_blank(), 
		text = element_blank(), axis.ticks.length = unit(0, "cm"),
		legend.position = "none", panel.margin = unit(0, "lines"),
		plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', face='italic'),
		axis.title=element_blank()
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	) +
	facet_wrap(~ species, ncol=4)
```

```{r, echo=FALSE, fig.width=4, fig.height=3.5, fig.cap="Species richness. Squares denote planning units. Planning units with a brighter color are inhabited by more species."}
# calculate species richness
grid.PLY$Species_richness <- grid.PLY@data %>%
	select(5:(4+n_distinct(spp.samples.DF$species))) %>% as.matrix() %>% rowSums()

# plot species richness
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat, 
		group=group, fill=Species_richness), color='grey10') +
	scale_fill_gradientn(name='Count (#)',
		colors=brewer.pal(9,'PuBu'),
		guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
	) +
	theme_classic() +
	theme(
		line = element_blank(), rect = element_blank(), 
		text = element_blank(), axis.ticks.length = unit(0, "cm"),
		legend.position = "none", panel.margin = unit(0, "lines"),
		plot.margin = unit(c(0, 0, 0, 0), "lines"),
		panel.border=element_rect(color='black', fill=NA, size=1)
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	) + 
	ggtitle('Species Richness')
```

```{r, echo=FALSE, fig.width=4, fig.height=3.5, fig.cap="Opportunity cost. Squares denote planning units. The color of each planning unit represents its opportunity cost (computed as total population density)"}
# plot opportunity costs
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat, 
		group=group, fill=pop.density), color='grey10') +
	scale_fill_gradientn(name='Cost',
		colors=brewer.pal(9, 'PuBu'),
		guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
	) +
	theme_classic() +
	theme(
		line = element_blank(), rect = element_blank(), 
		text = element_blank(), axis.ticks.length = unit(0, "cm"),
		legend.position = "none", panel.margin = unit(0, "lines"),
		plot.margin = unit(c(0, 0, 0, 0), "lines"),
		panel.border=element_rect(color='black', fill=NA, size=1)
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	) +
	ggtitle('Opportunity cost')
```

```{r, fig.width=8, fig.height=3.5, fig.cap='Climatic variation. Each panel depicts variation based on a different principle component (PC). Squares represent planning units. The color of each planning unit denotes the average PC value of pixels inside it. Planning units with more similar colors have more similar climate regimes.', echo=FALSE}
do.call(
	grid.arrange,
		append(
		llply(grep('^env\\_.*$', names(grid.DF), value=TRUE), function(x) {
			grid.FPLY$plot_title <- paste0('PC ', substr(x, nchar(x), nchar(x)))
			ggplot() +
				geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
					fill='grey85', color='grey70') +
				geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
					group='group', fill=x), color='grey10') +
				theme_classic() +
				theme(
					line = element_blank(), rect = element_blank(), 
					text = element_blank(), axis.ticks.length = unit(0, "cm"),
					legend.position = "none", panel.margin = unit(0, "lines"),
					plot.margin = unit(c(0, 0, 0, 0), "lines"),
					panel.border=element_rect(color='black', fill=NA, size=1),
					strip.background = element_rect(fill='grey20'),
					strip.text = element_text(color='white')
				) +
				coord_cartesian(
					xlim=buffered.range(grid.FPLY$long, 0),
					ylim=buffered.range(grid.FPLY$lat, 0)
				) +
				scale_fill_gradientn(name='',
					colors=brewer.pal(9, 'RdYlBu'),
					guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
				) +
				facet_wrap(~ plot_title)
		}),
		list(ncol=2)
	)
)
```

@@

```{r, echo=FALSE, fig.width=15, fig.height=14, fig.cap='Distribution of populations. Each panel depicts a different species. Squares denote planning units. Pie charts denote the location of sampled individuals, and colors denote the probability that they belong to different populations. Note that pie charts have been jittered to make individuals in close proximity visible.'}

@@

# create grobs
grobLST <- llply(
	seq_along(unique(pop.probs.DF$species)),

@@

@@

		# create base mapmap

@@

@@

@@

		pushViewport(viewport(layout=grid.layout(100,100)))
		vplayout <- function(x,y) viewport(layout.pos.row=x, layout.pos.col=y)
		print(curr.GROB, vp=vplayout(1:100,1:100))

@@

			curr.lat <- (curr.cell.DF$grid.latitude[1]-bbox['ll.lat'])/abs(bbox['ur.lat']-bbox['ll.lat'])

@@

			print(curr.pie, vp=viewport(x=curr.lon, y=curr.lat, width=0.05, height=0.05))

@@

```{r, echo=FALSE, fig.width=15, fig.height=14, fig.cap='Population membership probabilities. Each panel depicts a different species. Each vertical bar represents a different individual, and colors show the probability that it belongs to different populations. This type of plot is also known as a \texttt{Structure} plot.'}
# prepare data
pop.probs.DF <- ldply(
	seq_along(spp.StructureData.LST),
	function(i) {
		spp.Mclust.LST[[i]]$mclust$z
			as.data.frame() %>%
			mutate(Species=unique(spp.samples.DF$species)[i]) %>%
			gather(Population,Probability,-Species) %>%
			mutate(Population=as.numeric(gsub('V', '', Population, fixed=TRUE)),
				Individual=seq_along(Population)
				) %>%
			return()
	}
)
# make plot
ggplot(
		aes(x=Individual, y=Probability, fill=Population)
		data=pop.probs.DF) +
	geom_bar() +
	theme_classic() +
	theme(
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', face='italic'),

	) +
	xlab('') +
	ylab('Probability of population membership (%)') +
	facet_wrap(~ Species)
```

```{r, echo=FALSE}
plot.spp.nmds <- function(i) {
	## prepare data
	# get vector of adaptive and neutral column names
	adapt.col <- grep(
		paste0(unique(spp.samples.DF$species)[i], '_adaptive_d'),
		names(grid.FPLY), value=TRUE, fixed=TRUE
	)
	neutral.col <- grep(
		paste0(unique(spp.samples.DF$species)[i], '_neutral_d'),
		names(grid.FPLY), value=TRUE, fixed=TRUE
	)
	curr.FPLY <- grid.FPLY[,
		c(adapt.col, neutral.col,
		'long','lat','group'),drop=FALSE]
	curr.FPLY <- curr.FPLY %>% gather(d, value, contains('adaptive'), contains('neutral')) %>% mutate(
		d=gsub(paste0(unique(spp.samples.DF$species)[i], '_'), '', d, fixed=TRUE),
		d=gsub('_', ' ', d, fixed=TRUE)
	)
	for (j in seq_len(length(adapt.col)+length(neutral.col)))
		curr.FPLY[['d']] <- gsub(as.character(j), paste0('(', j, ')'), curr.FPLY[['d']], fixed=TRUE)
	curr.FPLY <- curr.FPLY %>% mutate(d=factor(gsub(' d(', ' (', d, fixed=TRUE)))
	# make plot
	ggplot() +
		geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
			fill='grey85', color='grey70') +
		geom_polygon(data=curr.FPLY, aes_string(x='long', y='lat', 
			group='group', fill='value'), color='grey10') +
		theme_classic() +
		theme(
			line = element_blank(), rect = element_blank(), 
			text = element_blank(), axis.ticks.length = unit(0, "cm"),
			legend.position = "none", panel.margin = unit(0, "lines"),
			plot.margin = unit(c(0, 0, 0, 0), "lines"),
			axis.title=element_blank(), strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white', size=20),
			legend.text = element_text(size=20)
		) +
		coord_cartesian(
			xlim=buffered.range(grid.FPLY$long, 0),
			ylim=buffered.range(grid.FPLY$lat, 0)
		) +
		scale_fill_gradientn(name='',
			colors=brewer.pal(9, 'RdYlBu'),
			guide=guide_colorbar(ticks=element_line(color='black'),
				border=element_line(color='black'), barheight=unit(7, 'cm'))
		) +
		facet_wrap(~ d, ncol=4)
}

>>>>

```{r, echo=FALSE, fig.width=9.5, fig.height=10, out.width='7.5in', out.height='8.5in', fig.cap='Species distributions. Squares represent planning units. For a given species, planning units that were found to be inhabited are denoted with bright blue.'}
## plot map of species distributions
# fortify data
spp.grid.FPLY <- ldply(unique(spp.samples.DF$species), function(x) {
		z <- grid.FPLY[,c('long', 'lat', 'group', x),drop=FALSE]
		names(z)[4] <- 'presence'
		z$species <- gsub('\\_', ' ', x)
		return(z)
	}
)
# plot species data
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spp.grid.FPLY, aes(x=long, y=lat, 
		group=group, fill=presence), alpha=0.8, color='grey10') +
	theme_classic() +
	guides(fill=guide_legend(title='Presence')) +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', face='italic'),
		axis.title=element_blank()
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	) +
	facet_wrap(~ species, ncol=4)
```

```{r, echo=FALSE, fig.width=4, fig.height=2.5, fig.cap="Species richness. Squares denote planning units. Planning units with a brighter color are inhabited by more species."}
# calculate species richness
grid.PLY$Species_richness <- grid.PLY@data %>%
	select(5:(4+n_distinct(spp.samples.DF$species))) %>% as.matrix() %>% rowSums()
# plot species richness
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat, 
		group=group, fill=Species_richness), color='grey10') +
	scale_fill_gradientn(name='Richness (#)',
		colors=brewer.pal(9,'PuBu'),
		guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
	) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
		panel.border=element_rect(color='black', fill=NA, size=1)
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	)
```

```{r, echo=FALSE, fig.width=4, fig.height=2.5, fig.cap="Opportunity cost. Squares denote planning units. The color of each planning unit represents its opportunity cost (computed as total population density)"}
# plot opportunity costs
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat, 
		group=group, fill=pop.density), color='grey10') +
	scale_fill_gradientn(name='Cost',
		colors=brewer.pal(9, 'PuBu'),
		guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
	) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
		panel.border=element_rect(color='black', fill=NA, size=1)
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	)
```

```{r, fig.width=8, fig.height=3.5, fig.cap='Climatic variation. Each panel depicts variation based on a different principle component (PC). Squares represent planning units. The color of each planning unit denotes the average PC value of pixels inside it. Planning units with more similar colors have more similar climate regimes.', echo=FALSE}
do.call(
	grid.arrange,
		append(
		llply(grep('^env\\_.*$', names(grid.DF), value=TRUE), function(x) {
			grid.FPLY$plot_title <- paste0('PC ', substr(x, nchar(x), nchar(x)))
			ggplot() +
				geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
					fill='grey85', color='grey70') +
				geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
					group='group', fill=x), color='grey10') +
				theme_classic() +
				theme(
					axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
					panel.border=element_rect(color='black', fill=NA, size=1),
					strip.background = element_rect(fill='grey20'),
					strip.text = element_text(color='white')
				) +
				coord_cartesian(
					xlim=buffered.range(grid.FPLY$long, 0),
					ylim=buffered.range(grid.FPLY$lat, 0)
				) +
				scale_fill_gradientn(name='',
					colors=brewer.pal(9, 'RdYlBu'),
					guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
				) +
				facet_wrap(~ plot_title)
		}),
		list(ncol=2)
	)
)
```

@@

```{r, echo=FALSE}

@@

# create function
plot.spp.pop.probs <- function(i) {

@@

	prop <- 0.85

@@

	# create base map grob

@@

			axis.title=element_blank(), axis.text=element_blank(),
			axis.line=element_blank(), axis.ticks=element_blank(),
			axis.ticks.length = unit(0, "cm"),

@@

	# create header grob
	curr.GROBH <- ggplot() +
			geom_text(aes(x=0,y=0,label=species),
				data=curr.spp.DF[1,,drop=FALSE],
				color='white', fontface='italic', size=4) +
			axis.title=element_blank(), axis.text=element_blank(),
			axis.line=element_blank(), axis.ticks=element_blank(),
			axis.ticks.length = unit(0, "cm"),
			panel.background=element_rect(fill='grey20')
		coord_cartesian(xlim=c(-1,1), ylim=c(-1,1))

@@

	pushViewport(viewport(layout=grid.layout(2,1, heights=unit(c(1-prop, prop), "npc"))))
	print(curr.GROBH, vp=viewport(layout.pos.row=1, layout.pos.col=1))
	print(curr.GROB, vp=viewport(layout.pos.row=2, layout.pos.col=1))

@@

		curr.lat <- ((curr.cell.DF$grid.latitude[1]-bbox['ll.lat'])/abs(bbox['ur.lat']-bbox['ll.lat']))*prop

@@

		print(curr.pie, vp=viewport(x=curr.lon, y=curr.lat, width=0.075, height=0.075))

@@

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_',' ',unique(spp.samples.DF$species)[1], fixed=TRUE),'} populations. Squares denote planning units. Pie charts denote quadrats where individuals were sampled, and colors denote the average probability that individuals in the quadrat belong to different populations on average.')}
plot.spp.pop.probs(1)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[2],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (2 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(2)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[3],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (3 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(3)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[4],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (4 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(4)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[5],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (5 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(5)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[6],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (6 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(6)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[7],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (7 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(7)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[8],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (8 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(8)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[9],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (9 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(9)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[10],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (10 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(10)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[11],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (12 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(11)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[12],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (12 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(12)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[13],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (13 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(13)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[14],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (14 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(14)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[15],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (15 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(15)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[16],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (16 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(16)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[17],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (17 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(17)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[18],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (18 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(18)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[19],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (19 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(19)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[20],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (20 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(20)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[21],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (21 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(21)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[22],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (22 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(22)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[23],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (23 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(23)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[24],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (24 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(24)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[25],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (25 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(25)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[26],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (26 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(26)
```

```{r, echo=FALSE, fig.width=3.5, fig.height=2.5, fig.cap=paste0('Distribution of \\textit{',gsub('_', ' ',unique(spp.samples.DF$species)[27],fixed=TRUE),'} populations. See Figure SX caption for conventions.')}
if (27 <= general.params.LST[[MODE]]$n.spp) plot.spp.pop.probs(27)
```

```{r, echo=FALSE}
plot.spp.nmds <- function(i) {
	## prepare data
	# get vector of adaptive and neutral column names
	adapt.col <- grep(
		paste0(unique(spp.samples.DF$species)[i], '_adaptive_d'),
		names(grid.FPLY), value=TRUE, fixed=TRUE
	)
	neutral.col <- grep(
		paste0(unique(spp.samples.DF$species)[i], '_neutral_d'),
		names(grid.FPLY), value=TRUE, fixed=TRUE
	)
	curr.FPLY <- grid.FPLY[,
		c(adapt.col, neutral.col,
		'long','lat','group'),drop=FALSE]
	curr.FPLY <- curr.FPLY %>% gather(d, value, contains('adaptive'), contains('neutral')) %>% mutate(
		d=gsub(paste0(unique(spp.samples.DF$species)[i], '_'), '', d, fixed=TRUE),
		d=gsub('_', ' ', d, fixed=TRUE)
	)
	for (j in seq_len(length(adapt.col)+length(neutral.col)))
		curr.FPLY[['d']] <- gsub(as.character(j), paste0('(', j, ')'), curr.FPLY[['d']], fixed=TRUE)
	curr.FPLY <- curr.FPLY %>% mutate(d=factor(gsub(' d(', ' (', d, fixed=TRUE)))
	# make plot
	ggplot() +
		geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
			fill='grey85', color='grey70') +
		geom_polygon(data=curr.FPLY, aes_string(x='long', y='lat', 
			group='group', fill='value'), color='grey10') +
		theme_classic() +
		theme(
			axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
			panel.border=element_rect(color='black', fill=NA, size=1),
			strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white', size=20)
		) +
		coord_cartesian(
			xlim=buffered.range(grid.FPLY$long, 0),
			ylim=buffered.range(grid.FPLY$lat, 0)
		) +
		scale_fill_gradientn(name='',
			colors=brewer.pal(9, 'RdYlBu'),
			guide=guide_colorbar(ticks=element_line(color='black'),
				border=element_line(color='black'), barheight=unit(7, 'cm'))
		) +
		facet_wrap(~ d, ncol=4)
}
